Robust Fault-Tolerant Control and Motion Planning of UAVs and Biped Robots Team System for Search and Rescue Usage

### 2022-10-20 paper/paper.tex
Add +Show folder. Can Plot URTS Senario.

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in S\&R is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupy map $\mathcal{C}$. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

@@

\section{simulation results}
In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy. First, a S\&R area divided into $N_T$ areas, $area_j,j=1,2,...,N$, is given as shown in Fig. \ref{fig:SR_area}. To simplify the description, we will focus on the UAV and robot in $1$st team. Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$. At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupy map and find targets. The search task is assumed to be obtained by dividing the unsearched region as shown in Fig. \ref{fig:S_task}. Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$. Suppose a target is found after a while as shown in Fig. \ref{fig:S_task}, at this point, we have a rescue task $T_6$. The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one. If the ground station assigns $\alpha_{1,5}$ and $\alpha_{2,2}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,5},T_2),(\alpha_{2,2},T_3) \})\cup\{ (\alpha_{1,5},T_6),(\alpha_{2,2},T_6) \}$. Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $j$th team is responsible for $j$th area, $area_j$}%
    \label{fig:SR_area}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining. The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinitions $q_{goal}$ (black dots in figure). For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths. For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption.}
    \label{fig:S_task}
\end{figure}

>>>>

The agents overall have the same system architecture in URTS except for some subprocess differences. Followed by the concept in \cite{paden2016survey}, a system architecture for an agent used in S\&R is proposed as shown in Fig. \ref{fig:sys}. The Simultaneous Localization And Mapping (SLAM) block converts sensor information into the location of agents $q_{start}$ and an occupancy map $\mathcal{C}$. The visual object recognition block provides distance information and object information through the analysis of sensor information. The object information provides agent machine vision that enables it to determine an appropriate behavior (e.g., a robot can see a obstacle and decides to climb through it). The detailed functions of remaining 5 blocks, i.e., Tack Allocation, Path Planning, Behavior Layer, Local Motion Planning and Tracking Control, will be explained in the following sections.

@@

\section{simulation results}
In this section, a specific S\&R procedure for URTS is given to illustrate the proposed UTRS system architecture and demonstrate the effectiveness of motion planning and control strategy. First, a S\&R area divided into $N_T$ areas, $area_j,j=1,2,...,N$, is given as shown in Fig. \ref{fig:SR_area}. To simplify the description, we will focus on the UAV and robot in $1$st team. Suppose each team has 5 agents, i.e., $N_A=5$, then we can denote $1$st team as a set, $team_1=\{ \alpha_{1,j} | j=1,2,...,5 \}$. At the beginning, the agents in $team_1$ are assigned the search tasks of $area_1$ to build the occupancy map and find targets. The search task is assumed to be obtained by dividing the unsearched region as shown in Fig. \ref{fig:S_task}. Representing the search tasks as a set, $task_1=\{ T_j | j=1,2,...,5 \}$, then the proper agent-task pairs can be obtained through the task allocation block, $allocation_1=\{ (\alpha_{1,j},T_j) | j=1,2,...,5 \}$. Suppose a target is found after a while as shown in Fig. \ref{fig:S_task}, at this point, we have a rescue task $T_6$. The new task list $task_2=task_1\cup\{ T_6 \}$ is obtained by updating the old one. If the ground station assigns $\alpha_{1,5}$ and $\alpha_{2,2}$ to perform $T_6$ through the task allocation algorithm, then we have the new allocation $allocation_2=(allocation_1-\{ (\alpha_{1,5},T_2),(\alpha_{2,2},T_3) \})\cup\{ (\alpha_{1,5},T_6),(\alpha_{2,2},T_6) \}$. Until the S\&R mission is over, the task allocation block will continuously work in the similar way.
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{An example of a S\&R area in URTS. This area is divided into $N_T$ areas, and $j$th team is responsible for $j$th area, $area_j$}%
    \label{fig:SR_area}
\end{figure}
\begin{figure}[htbp]
    \centering
    \includegraphics[scale=.42]{fig/1.pdf}\caption{The search tasks in $1$st team at the begining. The search tasks $T_j,j=1,2,...,5$ are to reach some consecutive destinitions $q_{goal}$ (black dots in figure). For robots, $q_{goal}$ will be passed to path planning block to find collision-free paths. For UAV, the sequence formed by $q_{goal}$ is directly the path $(\sigma_n)$ due to the no-collision assumption.}
    \label{fig:S_task}
\end{figure}
